Incentivizing Exploration by Heterogeneous Users

### 2018-06-05 algorithm_payment.tex
checked and edited lemma 7

\begin{lemma} \label{lem:no-incentives}
Fix an arm $i$.
Let $s \geq \exp(2/\MinProb)$, and let $\tau_s$ be the (random)
time when arm $i$ is pulled for the \Kth{s} time.
\dkedit{Let $\hat{x} = \frac{1}{2\Diam d}
  \cdot \min(\TieCutoff, \frac{\MinProb}{2\TieDensity})$.
Under \AccEU{\tau_s}{\hat{x}},}
this pull of arm $i$ is not incentivized.
\end{lemma}

@@

To make this intuition precise, we set
\dkedit{$x = x' = \frac{1}{2 \Diam d} \cdot \min(\TieCutoff, \frac{\MinProb}{2 \TieDensity})$}
(which is independent of the phase number $s$).
The cutoff point between early and late phases is now set to
$\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3}, \exp(\frac{2}{\MinProb}))$.
We will verify below that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
\leq \frac{n x}{2 \sigma}$
for all $n \geq \max(2, \frac{30 \sigma^3}{x^3})$.

Fix an arm $i$, and consider the \Kth{s} pull of arm $i$,
for $s \geq \EvenLaterPhase$.
If this pull occurred before phase $s$, it was definitely not incentivized.
So we condition on the pull occurring in phase $s$,
and let $\tau_s$ be the time step when this pull occurred;
notice that this means that this must be the first pull of arm $i$ in
phase $s$.

By Lemma~\ref{lem:round-prob} (with our choice of $x = x'$),
and a union bound over all $i,j$, we bound the probability
$\Prob{\AccEU{\tau_s}{x}}
\geq 1 - 24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$.
And by Lemma~\ref{lem:no-incentives},
under the event ${\mathcal E}_{\tau_s}(x)$,
arm $i$ is not payment-eligible.

Thus, for any $s \geq \EvenLaterPhase$,
the \Kth{s} pull of arm $i$ is incentivized  
with probability at most
$24 \ARMNUM d \cdot \exp \left(
\dkedit{  - \frac{1.8 s}{256 \Diam^2 d^2 \sigma^2}
  \cdot \min(\TieCutoff, \frac{\MinProb}{\TieDensity})^2}
\right)$.
Summing over all arms and phases $s$,
adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
the first \EvenLaterPhase phases, 
and using that $\exp(-x) \leq 1-x/2$ for $x \leq 1$,
the expected total number of arm incentivizations is at most
\begin{align*}
\lefteqn{\ARMNUM \EvenLaterPhase
  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
\dkedit{ - \frac{1.8}{256 \Diam^2 d^2 \sigma^2}
  \cdot \min(\TieCutoff, \frac{\MinProb}{\TieDensity})^2}
  \right)}}
\\ & = O\left( \max \left(
     \frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3},
\dkedit{     \frac{\ARMNUM \Diam^3 d^3 \sigma^3}{\TieCutoff^3},}
     \ARMNUM \exp \left(\frac{2}{\MinProb} \right) \right)
+ \max \left(
     \frac{\ARMNUM^2 d^3 \TieDensity^2 \sigma^2 \Diam^2}{\MinProb^2},
\dkedit{ \frac{\ARMNUM^2 d^3 \sigma^2 \Diam^2}{\TieCutoff^2}}
\right) \right)
\\ & = O\left( \ARMNUM \exp \left(\frac{2}{\MinProb}\right) \right).
\end{align*}

>>>>

\begin{lemma} \label{lem:no-incentives}
Fix an arm $i$.
Let $s \geq \exp(2/\MinProb)$, and let $\tau_s$ be the (random)
time when arm $i$ is pulled for the \Kth{s} time.
Let $\hat{x} = \frac{1}{2\Diam d}
  \cdot \min(\TieCutoff, \frac{\MinProb}{2\TieDensity})$.
Under \AccEU{\tau_s}{\hat{x}},
this pull of arm $i$ is not incentivized.
\end{lemma}

@@

To make this intuition precise, we set
$x = x' = \frac{1}{2 \Diam d} \cdot \min(\TieCutoff, \frac{\MinProb}{2 \TieDensity})$
(which is independent of the phase number $s$
\pfedit{and is equal to $\hat{x}$ defined in Lemma~\ref{lem:no-incentives}}).
\pfedit{We set} the cutoff point between early and late phases to
$\EvenLaterPhase = \max(2, \frac{30 \sigma^3}{x^3}, \exp(\frac{2}{\MinProb}))$.
We verify below that
$\sqrt{0.6 n \cdot \log (\log_{1.1}(n) + 1) + \frac{n x^2}{16 \sigma^2}}
\leq \frac{n x}{2 \sigma}$
for all $n \geq \max(2, \frac{30 \sigma^3}{x^3})$.

\pfdelete{
Fix an arm $i$, and consider the \Kth{s} pull of arm $i$,
for $s \geq \EvenLaterPhase$.
If this pull occurred before phase $s$, it was definitely not incentivized.
So we condition on the pull occurring in phase $s$,
and let $\tau_s$ be the time step when this pull occurred;
notice that this means that this must be the first pull of arm $i$ in
phase $s$.
}

\pfedit{Fix an arm $i$, let $s \geq \EvenLaterPhase$, and 
define $\tau_s$ as in Lemma~\ref{lem:no-incentives}.}
By Lemma~\ref{lem:round-prob} (with our choice of $x = x'$),
and a union bound over all $i,j$, we bound the probability
$\Prob{\AccEU{\tau_s}{x}}
\geq 1 - 24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$.
And by Lemma~\ref{lem:no-incentives},
under the event ${\mathcal E}_{\tau_s}(x)$,
arm $i$ is not payment-eligible.

Thus, for any $s \geq \EvenLaterPhase$,
the \Kth{s} pull of arm $i$ is incentivized  
with probability at most
$24 \ARMNUM d \cdot \exp \left(
- \frac{1.8 s}{\pfedit{64} \Diam^2 d^2 \sigma^2}
  \cdot \min(\TieCutoff, \frac{\MinProb}{\TieDensity})^2
\right)$.
Summing over all arms and phases $s$,
adding the at most $\ARMNUM \EvenLaterPhase$ incentivizations in
the first \EvenLaterPhase phases, 
and using that $\exp(-x) \leq 1-x/2$ for $x \leq 1$,
the expected total number of arm incentivizations is at most
\begin{align*}
\lefteqn{\ARMNUM \EvenLaterPhase
  + 24 \ARMNUM^2 d \cdot \frac{1}{1 - \exp \left(
- \frac{1.8}{\pfedit{64} \Diam^2 d^2 \sigma^2}
  \cdot \min(\TieCutoff, \frac{\MinProb}{\TieDensity})^2
  \right)}}
\\ & = O\left( \max \left(
     \frac{\ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3},
\frac{\ARMNUM \Diam^3 d^3 \sigma^3}{\TieCutoff^3},
     \ARMNUM \exp \left(\frac{2}{\MinProb} \right) \right)
+ \max \left(
     \frac{\ARMNUM^2 d^3 \TieDensity^2 \sigma^2 \Diam^2}{\MinProb^2},
\frac{\ARMNUM^2 d^3 \sigma^2 \Diam^2}{\TieCutoff^2}
\right) \right)
\\ & = O\left( \ARMNUM \exp \left(\frac{2}{\MinProb}\right) \right).
\end{align*}
